\ttitle

### 2013-05-23 Appendices/AppendixA-summaries.tex
working on algorithm section

>>>>

\subsubsection{Problem formulation}
[Not summarized here, useful for e.g. section \ref{statistical-framework}]

\subsubsection{SVCPD: The algorithm}
Instead of using statistical properties of the data, for each window of size $w$ a hyper-sphere is constructed without increasing computational complexity due to the \emph{kernel trick}.
The window size is related to the sensitivity of the method to change; small windows are sensitive with high false alarm rate whilst large windows are slow to detect change and have low alarm rates.
The algorithm is:

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  1 & Start with $n$ observations and construct hyper-sphere \\
  2 & Add next observation $x_t$ and drop first one \\
  3 & Identify new hyper-sphere and its \emph{approximate radius} \\
  4 & if $x_t$ is outside hyper-sphere, mark $t$ as change points and continue from step 2 \\
  5 & calculate radius average of last $w$ hyper-planes \\
  6 & calculate radius ratio $\hbar$. If lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point \\
  7 & continue from step 2 \\
  \hline
\end{tabular}
\caption{Support Vector machine based Change Point Detection algorithm}
\end{table}\end{center}

### 2013-05-23 Chapters/Chapter2.tex
Starting summary Peter Flach
working on algorithm section

\section{Statistical framework}
Many applications require the detection of time points at which the underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
Often this problem is formulated in a statistical framework, by inspecting the data generating PDF (Probability Density Function) of the time series data.
A change point is then defined as a significant change in the properties of the PDF, such as the mean and variance.

>>>>

\section{Statistical framework}\label{statistical-framework}
Many applications require the detection of time points at which the underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
Often this problem is formulated in a statistical framework, by inspecting the data generating PDF (Probability Density Function) of the time series data.
A change point is then defined as a significant change in the properties of the PDF, such as the mean and variance.
